A modern, event-based architecture for distributed evolutionary algorithms

### 2018-04-03 paper.tex
Explained a few things

  The evolutionary algorithm mapped over this architecture is 
  represented in Figure \ref{fig:kafkeo2}. The main
  design challenge is to try and map an evolutionary algorithm to a
  serverless, and then stateless, architecture. That part is done in
  points 1 through 5 of Figure \ref{fig:kafkeo2}. The beginning of the
  evolution is triggered from outside the serverless framework (1) by
  creating a series of Population objects, which we pack (2) to a message in the
  {\sf new-populations} {\em topic}. The arrival of a new population
  package sets off the {\sf MessageArrived} trigger (3), that is bound to
  the actions that effectively perform evolution. In this case we
  feature GA and PSO algorithms, although only GA has been implemented 
  for this paper. Any number of actions can be triggered in parallel by the same message,
  and new actions can be triggered while others are still working; this phase is
  then self-scaling and parallel by design.

@@

  This queue is polled by a service outside the serverless framework, called
  {\sf Population-Controller}. This service needs to be stateful, since
  it needs to wait until several populations are ready to then mix them (in
  step \#9 in Figure \ref{fig:kafkeo2}) to produce a new population, that is the result of selection
  and crossover between several populations coming from the {\sf
    evolved-population-objects} message queue. Eventually, these mixed
  populations are returned to the initial queue to return to the {\em
    serverless} part of the application. Another task of the 
    {\sf Population-Controller} is to start and stop the experiment. The service must
    keep the number of Population objects received, then after
    a certain number is reached, the controller stops sending new messages to the
    {\sf new-populations} {\em topic}. It is important to note, that because of
    the asynchronous nature of the system, several messages could still
    arrived after the current experiment is over. The controller must only
    accept messages belonging to the current process.

  % consists essentially on a single function, a single topic
  % in the MessageHub and a single kind of message, which includes a whole
  % population along with metadata. The function performs a series of
  % generations on the population, using a canonical algorithm with
  % mutation and crossover. If it finds the solution, in our case, the
  % minimum fitness, it sets a flag indicating it has found it so that it
  % propagates to different instances of the population; in any case, it
  % sends the whole evolved population as a message to the MessageHub, to
  % be propagated to the other instantiations on the function.

  This would be functionally equivalent to a sequential algorithm except
  for the fact that, between two calls to the {\sf get-new-populations}
  function, several
  population-messages have been received in the message queue. In fact,
  every call the {\sf Crossover-migrate} function receives several populations, which
  have to be merged to generate several new populations. This {\em merging} step
  before starting evolution takes the place of the {\em migration} phase
  and allows this type of framework to work in parallel, since several
  instances of the function might be working at the exact same time; the
  results of these instances are then received back by every one of the
  instances.

>>>>

  The evolutionary algorithm mapped over this architecture is 
  represented in Figure \ref{fig:kafkeo2}. The main
  design challenge is to try and map an evolutionary algorithm to a
  serverless, and then stateless, architecture. That part is done in
  points 1 through 5 of Figure \ref{fig:kafkeo2}. The beginning of the
  evolution is triggered from outside the serverless framework (1) by
  creating a series of Population objects, which we pack (2) to a message in the
  {\sf new-populations} {\em topic}. Population objects are the equivalent to islands or samples in EvoSpace. If Population object is a self-contained population of individuals, represented as a JSON structure.

  The arrival of a new population
  package sets off the {\sf MessageArrived} trigger (3), that is bound to
  the actions that effectively perform a small number of generations. In this case we give as an example a GA and a PSO algorithms, 
  although only the GA has been implemented 
  for this paper. Any number of GA algorithms ({\em actions}) can be triggered in parallel by the same message, and new actions can be triggered while others are still working; this phase is
  then self-scaling and parallel by design.

@@

  This queue is polled by a service outside the serverless framework, called
  {\sf Population-Controller}. This service needs to be stateful, since it implements a buffer that needs to wait until several populations are ready to then mix them (in step \#9 in Figure \ref{fig:kafkeo2}) to produce a new population, that is the result of selection
  and crossover between several populations coming from the {\sf
    evolved-population-objects} message queue. Eventually, these mixed
  populations are returned to the initial queue to return to the {\em
    serverless} part of the application. Another task of the 
    {\sf Population-Controller} is to start and stop the experiment. The service must
    keep the number of Population objects received, then after
    a certain number is reached, the controller stops sending new messages to the
    {\sf new-populations} {\em topic}. It is important to note, that because of
    the asynchronous nature of the system, several messages could still
    arrived after the current experiment is over. The controller must only
    accept messages belonging to the current process.
  % consists essentially on a single function, a single topic
  % in the MessageHub and a single kind of message, which includes a whole
  % population along with metadata. The function performs a series of
  % generations on the population, using a canonical algorithm with
  % mutation and crossover. If it finds the solution, in our case, the
  % minimum fitness, it sets a flag indicating it has found it so that it
  % propagates to different instances of the population; in any case, it
  % sends the whole evolved population as a message to the MessageHub, to
  % be propagated to the other instantiations on the function.

  %This would be functionally equivalent to a sequential algorithm except
  %for the fact that, between two calls to the {\sf get-new-populations}
  %function, several
  %population-messages have been received in the message queue. In fact,
  %every call the {\sf Crossover-migrate} function receives several
  %populations, which
  %have to be merged to generate several new populations. 
  This {\em merging} step
  before starting evolution takes the place of the {\em migration} phase
  and allows this type of framework to work in parallel, since several
  instances of the function might be working at the exact same time; the
  results of these instances are then received back by every one of the
  instances.
